Analysis for Biracial Grade Retention Project

### 2022-09-03 analysis/analysis.Rmd
Forgot manual weights on two marg commands

coefs_cf_ses <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df_ses, race==x)
  means_margin <- marg(model_full, "year", data=temp)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()

@@

coefs_cf_culture <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df_culture, race==x)
  means_margin <- marg(model_full, "year", data=temp)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()

>>>>

coefs_cf_ses <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df_ses, race==x)
  means_margin <- marg(model_full, "year", data=temp, weights=temp$perwt)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()

@@

coefs_cf_culture <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df_culture, race==x)
  means_margin <- marg(model_full, "year", data=temp, weights=temp$perwt)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()
